\subsection{Digital currency exchanges}\label{sec:exchanges}

Unless a person is running a node that participates in the mining process, the only other option when they want to get cryptocurrency, is to buy it from someone else. There is a multitude of options to purchase cryptocurrency, including cryptocurrency ATMs, companies that sell cryptocurrency with a PayPal account or a credit card, or specialised websites that enlist local people, who are willing to trade cryptocurrency for cash. However, the most popular option to buy cryptocurrency to date is to use a \acrfull{dce}. 

The principle of a \acrshort{dce} is that a person starts by registering on the website of the exchange and creating an online account. The person then proceeds by depositing some amount in fiat currency to the \acrshort{dce}, which can be done using a credit card, PayPal, bank transfer or other means. The amount transferred to the \acrshort{dce} is then credited to the person's online account. The person can use this account to exchange the credit for other crypto- or fiat currencies. After the exchange is completed, the person can withdraw the newly-acquired currency from the online-account to their own private wallet (in case of cryptocurrencies) or their bank account (in case of fiat currencies).

While the currency exchange process is usually the same across the different providers, the \acrshort{dce}s differ in fees, deposit and withdrawal speeds, or features. Typically, the fees range from 0.05\% to 1.5\% of the transaction volume, per transaction, with additional possible fees for deposit and withdrawal\footnotemark. The deposit and withdrawal speed range from instantaneous to couple of days, depending on the policy of the particular exchange.%
% 
\footnotetext{\url{https://crowdsourcingweek.com/blog/bitcoin-exchange-comparison/}, accessed 22-05-2018}
% 
Some \acrshort{dce}s require identity verification, before they allow users to trade, to prevent frauds and money laundering.\footnotemark
% 
\footnotetext{\url{https://www.bitstamp.net/faq/\#how-to-verify-your-personal-account}, accessed 22-05-2018}

Some of the most popular \acrshort{dce}s to date are: \textit{Coinbase}, \textit{Bitstamp}, \textit{CEX.IO}, \textit{eToro} or \textit{Binance}\footnotemark, all of them offering trading of Bitcoin, Ether and USD, while some also offering additional crypto- and fiat currencies.
% 
\footnotetext{\url{https://www.bestbitcoinexchange.io/}, accessed 22-05-2018}