\section{Background}\label{sec:background}
% 
In this section, we explain some of the main concepts used in this project. This section is needed to establish a common understanding behind these topics, so that unambiguous discussion can follow.

First, we briefly talk about the concept of currency and its exchange. Afterwards we define what a cryptocurrency is and how it differs from a fiat currency. At the end of this chapter, we describe two most popular cryptocurrencies Bitcoin and Ethereum.
% 
\input{04Background/01fiat_currency}
% 
\input{04Background/02cryptocurrency}
% 
\input{04Background/03blockchain}
% 
\input{04Background/04bitcoin}
% 
\input{04Background/05ethereum}

\subsection{Nomenclature}
Despite the existing definitions for words \textit{currency}, \textit{fiat currency} and \textit{cryptocurrency}, there are several naming convention in use today. This paragraph describes, which terms will be used further in this report.

The value of many cryptocurrencies is not backed by any commodity and it depends entirely on the supply/demand relationship. Therefore, by the definition, these cryptocurrencies are also fiat currencies. However, in the literature, the term \emph{fiat currency} is often used when referring to traditional, government issued currencies only. For the rest of this paper we will therefore keep this naming. Regular currencies, such as dollars, euros or crowns will be referred to as fiat currencies.

Virtual, digital money such as Bitcoins, Ether, Litecoin and similar are in minority of sources named `coin currencies'. However, in this paper they will be referred to as \textit{cryptocurrencies} instead, as this is the most common term.